Effects of the body force on the pedestrian and the evacuation dynamics

### 2020-02-07 paper.tex
mejoramos el resumen

The Social Force Model (SFM) is a suitable model for describing crowds behaviors.
In this research, we analyze the role of the body force in the original SFM. 
We focus on the parameter associated with the body stiffness ($k_n$) and its impact on the pedestrian dynamics in two different geometries: bottleneck and corridor.
Increasing $k_n$ produces opposite effects depending on the geometry analyzed. Pedestrians move faster in a bottleneck, but they move slower in corridors as $k_n$ increases. The improvement in the bottleneck geometry is because increasing the stiffness reduces the contacts among pedestrians. This effect reduces the number of blocking clusters close to the exit door (which is critical to improving the evacuation). The slow down in the corridor geometry occurs because when $k_n$ increases, the crowd behaves like a solid-granular-system in which the friction interaction with the wall determines the velocity of the whole crowd. We have also explored the dimensionless parameters that arise from the reduced-in-units equation of motion and tune them to reproduce the qualitative behavior of the empirical fundamental diagram.

@@

The presence of the FIF phenomenon for only ``soft'' individuals opens many questions 
on the microscopic dynamics of pedestrians. We may presume that contacts 
between pedestrians are quite different for soft individuals than for stiff 
individuals. Thus, we proceed to study the dynamics of contacting pedestrians, regardless of the overlap 
effects. We will assimilate the pedestrians as nodes and the whole crowd as a 
network. We will link any two individuals whenever they get in physical 
contact (\textit{i.e.} $r_{ij} \leq R_{ij}$).\\

>>>>

The Social Force Model (SFM) is a suitable model for describing crowd behaviors.
This research analyzes the role of the body force in the original SFM. 
We focused on the parameter associated to the body stiffness ($k_n$) and its impact on
the pedestrian dynamics for two different geometries: bottlenecks and corridors.
Increasing $k_n$ produces opposite effects on either geometry: an increase of the 
crowd velocity for bottlenecks, and a decrease for corridors. 
The former reflects the fact that stiffness reduces the overlaps and the sliding friction
among pedestrians. This reduces the number of blocking cluster close
to the exit door.  The corridor, instead, tights the pedestrians into a lattice-like configuration
due to space limitations. The friction interaction with the walls determine the velocity
of the whole crowd along the corridor. 
Additionally, the corridor geometry experiences a flux slowing down for very crowded environments,
as observed in many real-life situations.
We also explored the dimensionless parameters that arise from the reduced-in-units equation 
of motion and tuned them to reproduce the qualitative behavior of the empirical fundamental diagram.

@@

The existence of the FIF phenomenon for only ``stiff'' individuals opens many questions 
on the microscopic dynamics of pedestrians. We may presume that contacts 
between pedestrians are quite different for soft individuals than for stiff 
individuals. Thus, we proceed to study the dynamics of contacting pedestrians, regardless of the overlap 
effects. We will assimilate the pedestrians as nodes and the whole crowd as a 
network. We will link any two individuals whenever they get in physical 
contact (\textit{i.e.} $r_{ij} \leq R_{ij}$).\\
